---
title: "Appendix A"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(ggplot2)
library(rpart)
library(rpart.plot)
```

Load table in and add a column that calculate the percentage of total followers each subject gained over the 90-day period.
```{r }
tab <- read.csv("TwitterData.csv")

tab <- tab %>%
  mutate(Percent.Follower.Change = 100 * Follower.count.slope.over.90.days.after.scandal / Total.Followers)

tab
```

Group the data by industry, calculate mean percentage change and plot it.
```{r 2}
new_tab <- tab %>%
  select(Person, Industry, Percent.Follower.Change) %>%
  filter(Person != "Roseanne Barr" & Person != "Daryl Morey") %>%
  group_by(Industry) %>%
  summarise(avg_change = mean(Percent.Follower.Change))

new_tab %>%
  ggplot(aes(x = Industry, y = avg_change, fill=Industry)) +
  geom_bar(stat="identity") +
  ylab("Average percent change in Twitter followers") + 
  ggtitle("Average Percent Change in Twitter Followers by Industry")
```

Look at those subjects involved in sexual assault...
```{r 3}
new_tab <- tab %>%
  filter(Description=="Sexual assault") %>%
  select(Person, Description, Industry, Gain.Lost, Percent.Follower.Change)

new_tab
```

... versus everyone else.
```{r 4}
new_tab <- tab %>%
  filter(Description!="Sexual assault") %>%
  select(Person, Description, Industry, Gain.Lost, Percent.Follower.Change)

new_tab
```

Inspect subject's latency against other information, if applicable.
```{r 5}
new_tab <- tab %>%
  select(Person, Description, Gain.Lost, Latency, Total.Followers) %>%
  filter(!is.na(Latency))

new_tab
```

Train a decision tree to predict what percentage change a subject will see, based on the type of scandal (Sexual assault, Tweet-related, or Other) and the subject's industry.
```{r 6}
input <- tab %>%
  mutate(Sexual.Assault = (Description=="Sexual assault")) %>%
  mutate(Desc = 
           ifelse(Description=="Sexual assault", 
                  "Sexual assault",
                  ifelse(Description=="Offensive tweet" | Description =="Racist tweet",
                         "Tweet",
                         "Other")))

binary.model <- rpart(
  Percent.Follower.Change ~ Desc + Industry,
  data = input,
  method = "anova",
  control = rpart.control(minbucket=1, minsplit=1)
)
binary.model
rpart.plot(binary.model, extra = 1, type = 3)
```
